---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# ecbr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/m-muecke/ecbr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/m-muecke/ecbr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

ecbr is a minimal R client for the [ECB API](https://data.ecb.europa.eu/help/api/overview).

## Installation
You can install the development version of ecbr from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("m-muecke/ecbr")
```

## Usage

```{r demo, message = FALSE}
library(ecbr)

# fetch US dollar/Euro exchange rate
fx_rate <- ecb_data("EXR", "D.USD.EUR.SP00.A", start_period = "2021-01-01")
fx_rate
```

```{r plotting, message = FALSE, echo = FALSE, dpi = 300}
library(ggplot2)

title <- tools::toTitleCase(fx_rate[1, "title", drop = TRUE])
subtitle <- fx_rate[1, "description", drop = TRUE]

ggplot(fx_rate, aes(x = date, y = value)) +
  geom_line() +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.major.y = element_line(color = "black", linewidth = 0.2),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "black"),
    axis.title = element_blank()
  ) +
  scale_y_continuous(labels = scales::label_currency()) +
  labs(title = title, subtitle = subtitle)
```

## Related work
* [ecb](https://github.com/expersso/ecb): R interface to the European Central Bank's Statistical Data Warehouse (SDW) API.
* [rsdmx](https://github.com/opensdmx/rsdmx): R package for reading SDMX data and metadata.
* [readsdmx](https://github.com/mdequeljoe/readsdmx): R package for reading SDMX data and metadata.
* [pdfetch](https://github.com/abielr/pdfetch): R package for downloading economic and financial time series from public sources.
